Multi-scale assessment of a grassland productivity model

### 2020-12-27 manuscript/manuscript.Rmd
clarify text in fig 3/4 legends

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Observed and predicted fCover values of the All Site model using all available data, and the three vegetation type models each using all PhenoCam sites with an ROI in the respective vegetation type. NSE is the average Nash Sutcliffe coefficient of efficiency among sites, and \textit{F} is the mean coefficient of variation of the mean absolute error. The correlation line (blue) represents the overall trend in predicted versus observed values, while the 1:1 line (red) represents a perfect fit."}
knitr::include_graphics("figs/allsite_veg_errors.png")
```

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Observed and predicted fCover values for seven model iterations where only sites with a specified vegetation type within a single ecoregion were used in model fitting. NSE is the average Nash Sutcliffe coefficient of efficiency among sites, and \textit{F} is the mean coefficient of variation of the mean absolute error. The correlation line (blue) represents the overall trend in predicted versus observed values, while the 1:1 line (red) represents a perfect fit."}
knitr::include_graphics("figs/ecoregion_vegtype_errors.png")
```

>>>>

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Observed and predicted daily fCover values of the All Site model and the three vegetation type models, each using all available sites and years with the respective spatial scale. NSE is the average Nash Sutcliffe coefficient of efficiency among sites, and \\textit{F} is the mean coefficient of variation of the mean absolute error. The correlation line (blue) represents the overall trend in predicted versus observed values, while the 1:1 line (red) represents a perfect fit."}
knitr::include_graphics("figs/allsite_veg_errors.png")
```

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Observed and predicted daily fCover values for models from seven spatial scales, where only specific vegetation types within a single ecoregion were used in model fitting. Each uses all available sites and years with the respective spatial scale. NSE is the average Nash Sutcliffe coefficient of efficiency among sites, and \\textit{F} is the mean coefficient of variation of the mean absolute error. The correlation line (blue) represents the overall trend in predicted versus observed values, while the 1:1 line (red) represents a perfect fit."}
knitr::include_graphics("figs/ecoregion_vegtype_errors.png")
```
